Estimating nucleon substructure properties in a\\[.2ex] unified model of p-Pb and Pb-Pb collisions

### 2018-05-09 talk/qm2018.tex
Work on MAP figure

\begin{frame}{\scshape Collectivity in small systems, is it flow?}
  \smallskip
  \begin{columns}[T]
    \begin{column}{.62\textwidth}
      \bigskip
      Important questions:\\
      \begin{itemize}
        \item Is hydro applicable to small collision systems?
        \item If so, can we describe small system collectivity using current hydro models?
      \end{itemize}
      \smallskip
      First question precludes the second, but also more difficult to answer.\\[1ex]
      Let's tackle the second question \textit{assuming} hydrodynamic models make
      sense down to length scales $\Delta x=.2$~fm.\\[1ex]
      Under this assumption, does a unified hydrodynamic description of p+A and A+A data exist?
    \end{column}
    \begin{column}{.3\textwidth}
      \centering
      \includegraphics[width=\columnwidth]{pbpb_corr2d}\\
      \includegraphics[width=\columnwidth]{ppb_corr2d}
    \end{column}
  \end{columns}

@@

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.98\paperheight]{posterior}
    };
    \node[anchor=north, xshift=3cm, yshift=-.5cm] (title) at (current page.north) {
      \color{theme}{\scshape \Large Bayesian posterior}
    };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
      };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
      };
    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (2.6, .8);

@@

    \node<2>[xshift=0cm, yshift=0cm, scale=.3] {
      \includegraphics[scale=.15]{magnifying-glass}
    };
    \node<2>[below=.4cm of title, align=center] {
        \includegraphics[width=.5\textwidth]{posterior_p}\\[1ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[.5ex]
        $dS/dy \sim \sqrt{T_A T_B}$
      };
    %\node<3>[xshift=-1.05cm, yshift=1.5cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    %\node<3>[below=.4cm of title, align=center] {
    %    \includegraphics[width=.5\textwidth]{posterior_parton_number}\\[2ex]
    %    \small Evidence for nucleon substructure, $N_\text{partons} > 1$.\\
    %    \small Does not prefer a specific constituent number.
    %  };
    %\node<4>[xshift=-1.6cm, yshift=1.0cm, scale=.3] {\includegraphics[scale=.15]{magnifying-glass}};
    %\node<4>[below=.4cm of title, align=center] {
    %    \includegraphics[scale=.7]{proton_posterior_shape}\\[2ex]
    %  };
  \end{tikzpicture}
\end{frame}

\begin{frame}{\scshape Nucleon size and shape}
  \begin{columns}
    \begin{column}{.45\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{proton_posterior_shape}
      \end{figure}
    \end{column}
    \begin{column}{.55\textwidth}
      \begin{itemize}
        \item Parton sampling radius,\\[.5ex]
          $\sigma_\mathrm{const} = 0.99_{-0.15}^{+0.17}$~fm\\[2ex]
        \item Parton (Gaussian constituent) width,\\[.5ex]
          $w_\mathrm{const} = 0.47_{-0.15}^{+0.20}$~fm\\[2ex]
        \item Results likely sensitive to model details,
          e.g.\ equation of state, pre-equilibrium dynamics and viscous
          corrections $\delta f$\\[2ex]
      \end{itemize}
    \end{column}
  \end{columns}
\end{frame}

\begin{frame}{\scshape QGP medium properties}
  \begin{figure}
    \includegraphics[width=.9\textwidth]{region_shear_bulk}
  \end{figure}
  \begin{center}
    Pb-Pb at 2.76 and 5.02 TeV, better constraint on $\eta/s$ than p-Pb and Pb-Pb at 5.02 TeV
  \end{center}
\end{frame}

\begin{frame}{\scshape Maximum a posteriori parameters}
  \begin{center}
    \Large To do if time allows...
  \end{center}
\end{frame}

>>>>

\begin{frame}{\scshape Collectivity in small systems, is it flow?}
  \smallskip
  \begin{columns}[T]
    \begin{column}{.62\textwidth}
      \bigskip
      Important questions:\\
      \begin{itemize}
        \item Is hydro applicable to small collision systems?
        \item If so, can small system collectivity be described using current hydro models?
      \end{itemize}
      \smallskip
      First question precludes the second, but also more difficult to answer.\\[1ex]
      Let's tackle the second question \textit{assuming} hydrodynamic models make
      sense down to length scales $\Delta x=.2$~fm.\\[1ex]
      Under this assumption, does a unified hydrodynamic description of p+A and A+A data exist?
    \end{column}
    \begin{column}{.3\textwidth}
      \centering
      \includegraphics[width=\columnwidth]{pbpb_corr2d}\\
      \includegraphics[width=\columnwidth]{ppb_corr2d}
    \end{column}
  \end{columns}

@@

\begin{frame}[plain]
  \begin{tikzpicture}[remember picture, overlay]
    \node[anchor=west] at (current page.west) {
      \includegraphics[height=.98\paperheight]{posterior}
    };
    \node<1>[anchor=north, xshift=3cm, yshift=-.5cm] (title) at (current page.north) {
      \color{theme}{\scshape \Large Bayesian posterior}
    };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.4cm of title] (b1) {%
      \small One row (column) for each parameter
    };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b1] (b2) {%
      \small Diagonal panels: marginal distribution of a single model parameter
    };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.1cm of b2] (b3) {%
      \small Off-diagonal panels: joint distribution between a pair of model parameters
    };
    \node<1>[draw=none, text width=6.5cm, align=left, below=.2cm of b3] (b4) {%
      \textcolor{theme}{Let's look at some specific regions...}
    };

    \draw<1>[->, thick, theme] (b2.west) to [out=180, in=90] (2.6, .8);

@@

    \node<2>[xshift=1cm, yshift=2.1cm] {
      \includegraphics[scale=.065]{magnifying-glass}
    };
    \node<2>[anchor=north east, align=center, inner sep=.6cm] (post_p) at (current page.north east){
        \includegraphics[width=.6\textwidth]{posterior_p}\\[1ex]
        \small Initial entropy deposition\\
        \small consistent with geometric mean\\[1ex]
        $dS/dy \sim \sqrt{T_A T_B}$
    };
    \node<3>[xshift=2.7cm, yshift=0.5cm] {
      \includegraphics[scale=.065]{magnifying-glass}
    };
    \node<3>[anchor=north east, inner sep=.8cm, align=center] at (current page.north east) {
        \includegraphics[width=.5\textwidth]{posterior_parton_number}\\[2ex]
        No strong preference for a specific\\
        constituent number
    };
    \node<3>[align=center] (disfavor) at (6, 2) {
        One constituent\\
        (no substructure) disfavored
    };
    \draw<3>[->, thick, theme] (disfavor.south) to [out=-90, in=90] (7.55, -1.2);
    \node<4>[xshift=2.15cm, yshift=0cm] {
      \includegraphics[scale=.065]{magnifying-glass}
    };
    \node<4>[anchor=east] (proton) at (current page.east) {
      \includegraphics[width=.5\textwidth]{proton_posterior_shape}
    };
    \node<4>[xshift=-3.2cm, yshift=-1.6cm, align=right] (proton_label) at (proton.north west) {
      Informative posterior on constituent\\
      sampling radius $r$ and width $w$\\[2ex]
      $r=0.99_{-0.15}^{+0.17}$~fm\\[1ex]
      $w=0.47_{-0.15}^{+0.20}$~fm
    };
    \node<5>[anchor=north east, inner sep=.8cm, align=center] at (current page.north east) {
      \includegraphics[width=.6\textwidth]{region_shear}
    };
    \node<6>[anchor=north east, inner sep=.8cm, align=center] at (current page.north east) {
      \includegraphics[width=.6\textwidth]{region_bulk}
    };
  \end{tikzpicture}
\end{frame}

%\begin{frame}{\scshape QGP medium properties}
%  \begin{figure}
%    \includegraphics[width=.9\textwidth]{region_shear_bulk}
%  \end{figure}
%  \begin{center}
%    Pb-Pb at 2.76 and 5.02 TeV, better constraint on $\eta/s$ than p-Pb and Pb-Pb at 5.02 TeV
%  \end{center}
%\end{frame}

\begin{frame}[plain]
  \begin{columns}
    \begin{column}{.5\textwidth}
      Right: maximum a posteriori (best fit) predictions from the calibrated emulator; \emph{not a model calculation}.\\[2ex]
      \begin{tabular}{ll}
        norm           & 20.7 \\
        $p$            & 0.0314 \\
        $\sigma_\text{fluct}$  & 0.835 \\
        $r$      & 0.903 \\
        $n$ partons  & 6.48 \\
        $\chi$  & 0.288 \\
        $d_\text{min}^3$          & 1.11 \\
        $\tau$ fs         & 0.595 \\
        $\eta/s$ min       & 0.122 \\
        $\eta/s$ slope     & 0.742 \\
        $\eta/s$ crv       & -0.203 \\
        $\zeta/s$ max      & 0.0510 \\
        $\zeta/s$ width    & 0.0275 \\
        $\zeta/s$ $T_0$       & 0.185 \\
        $T_\text{sw}$        & 0.143
      \end{tabular}
    \end{column}
    \begin{column}{.4\textwidth}
      \includegraphics[height=.95\textheight]{find_map}
    \end{column}
  \end{columns}
\end{frame}
